---
title: "Developing Data Products Course Project"
date: "1/1/2017"
output: ioslides_presentation
---


## Introduction

- This presentation is for the Developing Data Products course offered by Coursera.

- The Shiny application can be found here: https://drbass89.shinyapps.io/dataproducts/

- The source code is available here: https://github.com/datmuzik/DataProducts

## Application

The app developed allows you to select the number of bins used in building a histogram of the MPG variable in the mtcars dataset.

## ui Code

```{r ui code, eval=FALSE, echo=TRUE}
 #Sidebar with a slider input for number of bins 
  sidebarLayout(
    sidebarPanel(
      h3("Please select number of bins for MPG histogram"),
      sliderInput("bins",
                   "Number of bins:",
                   min = 1,
                   max = 50,
                   value = 30)
    ),
```

## Server Code

The app takes the selected bin value and creates a histogram for MPG using the mtcars dataset:

```{r cars, eval=FALSE, echo = TRUE}
  x <- mtcars[, 1] 
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  
  hist(x, breaks = bins, col = 'darkgray', border = 'white', main='Histogram of MPG')
```



